Understanding Factors Contributing to Application Approval in Urban Planning Decisions (2016-2024)

### 2024-12-04 paper/paper.qmd
Final Revision

Our data [@committee_application] was extracted from opendatatoronto [@opendatatoronto]. This dataset focuses on applications submitted to the City of Toronto's Committee of Adjustment, a governing body responsible for reviewing minor variance and consent applications related to land use and development. These applications are submitted by property owners and developers seeking permission to deviate from existing zoning regulations or to subdivide land. The Committee’s decisions—whether to approve or refuse an application—have significant implications for urban development, community planning, and city growth.

@@

posterior_vs_prior(model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

>>>>

The data about Committee of Adjustment Applications [@committee_application] was extracted from Open Data Toronto [@opendatatoronto]. This dataset focuses on applications submitted to the City of Toronto's Committee of Adjustment, a governing body responsible for reviewing minor variance and consent applications related to land use and development. These applications are submitted by property owners and developers seeking permission to deviate from existing zoning regulations or to subdivide land. The Committee’s decisions—whether to approve or refuse an application—have significant implications for urban development, community planning, and city growth.

@@

posterior_vs_prior(model) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(hjust = 1, vjust = 0.5),
    text = element_text(size = 6)
  ) +
  guides(color = guide_legend(ncol = 6)) +
  theme(legend.position = "bottom") +
  coord_flip()
```
